### 2018-07-17 Manuscripts/cog-psych/revision/methods_results_e3.tex
Added representativeness to manuscript. Updated figures and results. Discussion in various places and some reviewer-related responses still need work.

% \begin{document}
\section{Experiment 3}
Experiments 1 and 2 clearly establish the importance of contrast in category generation. Follow-up model-based analyses illustrated that both contrast models account for participant performance better than models that do not take into account contrast. We also found more support for contrast as representativeness hypothesis over contrast as exemplar dissimilarity hypothesis.

Although category generation is an intriguing aspect of human cognition, it has played a relatively limited role in the broader categorization literature. To establish that contrast plays a broader role in categorization, we conducted a traditional category learning study. In it, participants learned two categories, where the categories learned by each participant in Experiment 3 was yoked to the Alpha shown and Beta generated by each participant in Experiment 2. If contrast plays a broader role in categorization, then Beta categories rated as "better" according to the contrast models should be easier for participants to learn.

@@

\subsection{Results}

@@

Overall accuracy of the participants was high, with a mean error rate of $.19$
($SD = .19$; min max?). Error rates for each block are presented in Figure
\ref{fig:learningcurve}.

@@

In the previous section (or Section X.X), we demonstrated that the best
performing models were the two contrast models. In this section, our goal is to
investigate if contrast is also important in category learning tasks.

It is also the
goal of this paper to demonstrate that there is an association between the
model's [justifying the errorvscat plot is harder than I thought] To compare the
performances of each model, we analysed the correlation between each model's fit
to a participant's unique category set and the participant's error rate.
Intuitively, a well-performing model should be able to closely fit (i.e., easily
generate) A positive correlation would indicate that the model is We used the
same set of optimised parameters found from Section X.X, with individual values
for selective attention.

\begin{figure}
    \begin{center}
    \includegraphics[width=\textwidth]{figs/perror_corr.pdf}
    \caption{Correlation between observed participant error and model fit.}
    \label{fig:perror_corr}
    \end{center}
\end{figure}

@@

The specific reason for why contrast as implemented in PACKER is superior to
contrast as implemented in the representativeness model is still not clear.

[Note Joe's comments on figure formatting (font size, remove redundant y-axes,
etc)]

>>>>

% \begin{document}
\section{Experiment 3}

Experiments 1 and 2 clearly establish the importance of contrast in category
generation. Follow-up model-based analyses illustrated that both contrast models
account for participant performance better than models that do not take into
account contrast. We also found more support for contrast as representativeness
hypothesis over contrast as exemplar dissimilarity hypothesis.

\sxlnote{I felt like there could be a little more explanation in terms of
  justifying this experiment so I added an extra sentence (the second last in
  the following paragraph) - I don't have too strong feelings about it so please
  feel free to remove if you think it's too much. Also see the footnote
  addressing the paper's lack of category learning fits. It's a bit of a cop
  out, but entirely true!}

Although category generation is an intriguing aspect of human cognition, it has
played a relatively limited role in the broader categorization literature. To
establish that contrast plays a broader role in categorization, we conducted a
traditional category learning study. In it, participants learned two categories,
where the categories learned by each participant in Experiment 3 was yoked to
the Alpha shown and Beta generated by each participant in Experiment 2. Our goal
is to investigate whether model performance (in generating categories) is
consistent with human performance (in learning those categories).\footnote{It is
  possible to adjust the present models of category generation such that they
  can make category learning predictions. However, such an adjustment makes the
  strong assumption that the very same processes governing category generation
  also apply to category learning. Taking this approach would fall outside the
  scope of the current investigation.} Specifically, if contrast plays a
broader role in categorization, then Beta categories rated as "better" according
to the contrast models should be easier for participants to learn.

@@

\subsection{Results and Analysis}

@@

Overall accuracy of the participants was high, with a mean error rate of $.19$
($SD = .19$). Error rates for each block are presented in Figure
\ref{fig:learningcurve}.

@@

In order to analyze the consistency between model and human performance, we
optimized each model such that the Pearson correlation between the model's
negative log-likelihood of generating each unique category set and the
participant's error in learning that category set is maximized. As with the
analysis in Section \ref{section:individual-diff}, we simulated the weighting of
each dimension independently depending on the generated categories.

The greatest correlations were observed when fitting with the contrast models.
Specifically, PACKER correlated with human performance with
$r = .65, 95\% CI$\footnote{Confidence intervals were obtained using a bootstrap
  method with 1000 bootstrap samples.}$ [.47,.78]$, and the representativeness
model correlated with human performance with $r = .56, 95\% CI [.38, .72]$.
Copy-and-tweak yielded a correlation of $r = .45, 95\% CI [.29, .61]$ and the
hierarchical Bayesian model yielded a similar correlation of
$r = .46, 95\% CI [.30, .61]$. These results are graphically presented in Figure
\ref{fig:perror_corr}.

\begin{figure}
    \begin{center}
    \includegraphics[width=\textwidth]{figs/modelvspptp.pdf}
    \caption{Scatterplots indicating the correlations between observed
      participant error and model fit. Blue discontinuous line are best-fit
      lines. Green discontinuous lines indicate boundaries generated by the 95\%
      CI around the fitted correlations. }
    \label{fig:perror_corr}
    \end{center}
\end{figure}

@@
